Resonance Fourier Transform:\\ Unitary Lens for Compression, Crypto,\\ and Quantum-Inspired Computing

### 2025-11-26 papers/paper.tex
Organize repository structure - move documentation, papers, and scripts
- Moved reference docs to docs/reference/:
  * ASSEMBLY_RFT_TEST_RESULTS.md
  * PAPER_VALIDATION_PLAN.md
  * RFT_FRAMEWORK_SUMMARY.md
  * UPDATE_VERIFICATION_CHECKLIST.md

- Moved paper assets to papers/:
  * IEEEtran.bst, IEEEtran.cls
  * quantoniumos_rft.bib
  * paper.tex, paper.pdf
  * coherence_free_hybrid_transforms.tex/pdf

- Moved scripts to scripts/:
  * compile_paper.sh, push_cleanup.sh
  * generate_all_theorem_figures.py
  * run_paper_validation_suite.py
  * run_quick_paper_tests.py

- Cleaned temporary files:

\title{The Resonance Fourier Transform (RFT):\\
Unitary Lens for Compression, Crypto,\\
and Quantum-Inspired Computing}

\author{
  Luis M.~Minier\\
  Independent Researcher\\
  Email: \texttt{luisminier79@gmail.com}\\
  GitHub: \url{https://github.com/mandcony/quantoniumos}\\
  DOI: \href{https://doi.org/10.5281/zenodo.17712905}{10.5281/zenodo.17712905}
}

@@

This paper takes the position that, if we want a single transform backbone to serve compression, crypto-like mixing, and quantum-inspired simulation, we have to leave the integer grid and the flat circle behind. We therefore introduce the \emph{Resonance Fourier Transform} (RFT): a unitary family of transforms built on irrational, golden-ratio--based phase progressions and braided toroidal topologies, with a canonical QR-derived $\Phi$-RFT for theory and a closed-form fast $\Phi$-RFT for practice. On top of this basis, we build: (i) a rigorously validated stack of $\Phi$-RFT theorems covering unitarity, complexity, sparsity, and twisted-convolution algebra; (ii) a hybrid DCT+RFT codec that beats single-basis baselines on mixed-structure signals; (iii) an RFT-SIS experimental lattice playground with measured avalanche/diffusion; and (iv) a unified C/FPGA execution path that removes Python from the hot loop and demonstrates that this resonance-based approach is not just mathematically consistent, but also system-level executable.

>>>>

\title{Resonance Fourier Transform:\\
Unitary Lens for Compression, Crypto,\\
and Quantum-Inspired Computing}

\author{
  Luis M.~Minier\\
  QuantoniumOS Research Team, Independent Researcher\\
  Email: \texttt{luisminier79@gmail.com}\\
  GitHub: \url{https://github.com/mandcony/quantoniumos}\\
  DOI: \href{https://doi.org/10.5281/zenodo.17712905}{10.5281/zenodo.17712905}
}

@@

The Resonance Fourier Transform (RFT) was introduced and formally analyzed in~\cite{minier2025rft} (DOI: 10.5281/zenodo.17712905) as a unitary family of transforms built on irrational, golden-ratio--based phase progressions and braided toroidal topologies, with a canonical QR-derived $\Phi$-RFT for theory and a closed-form fast $\Phi$-RFT for practice. This paper extends that foundational work by demonstrating RFT's practical application in hybrid compression, cryptographic mixing, and quantum-inspired computing. On top of this basis, we build: (i) a rigorously validated stack of $\Phi$-RFT theorems covering unitarity, complexity, sparsity, and twisted-convolution algebra; (ii) a hybrid DCT+RFT codec that beats single-basis baselines on mixed-structure signals; (iii) an RFT-SIS experimental lattice playground with measured avalanche/diffusion; and (iv) a unified C/FPGA execution path that removes Python from the hot loop and demonstrates that this resonance-based approach is not just mathematically consistent, but also system-level executable.
